---
title: Mika Braginsky
output:
  html_document:
    self_contained: false
    theme: cosmo
    css:
      - css/solarized.css
      - css/bs-callout.css
      - css/index.css
    includes:
      in_header: header.html
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
library(shiny)
library(glue)
library(purrr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
tagList(rmarkdown::html_dependency_font_awesome())

components <- yaml::read_yaml("components.yaml")
```

<div class="container">
```{r, header}
tags$header(
  fluidRow(
    column(width = 4, h2("Mika Braginsky")),
    column(
      width = 3, align = "center",
      tags$small(
        p("Pronouns: ", span(id = "pronouns", "they/them")),
        p("Email: ", a(id = "email")))
    ),
    column(
      width = 5, align = "right",
      tags$nav(
        tags$ul(
          class = "nav nav-pills pull-right",
          tags$li(
            role = "presentation",
            a(href = "https://github.com/mikabr", icon("github"), "GitHub")
          ),
          tags$li(
            role = "presentation",
            a(href = "files/mikabr-cv/mikabr-cv.pdf", icon("address-card"), "CV")
          ),
          tags$li(
            role = "presentation",
            a(href = "https://scholar.google.com/citations?user=VNAMYHMAAAAJ",
              icon("folder-open"), "Papers")
          )
        )
      )
    )
  )
)
```

I'm a software developer at the [Language and Cognition Lab](https://langcog.stanford.edu/) at Stanford University. I work on tools and resources for **data sharing** and other **open science practices**.

Previously, I was a postdoctoral scholar at the [Quantitative Sciences Unit](https://med.stanford.edu/qsu.html) at Stanford University, where I worked with [Maya Mathur](https://www.mayamathur.com) on tools for **reducing bias in meta-analysis** and on studies of interventions for 
**reducing meat consumption**.

Before that I got my PhD in [Brain and Cognitive Sciences](http://bcs.mit.edu) at MIT, where I studied **how kids learn words and word structure**. I was advised by [Ted Gibson](http://tedlab.mit.edu/people.html) and also collaborated extensively with [Mike Frank](http://web.stanford.edu/~mcfrank/), [Virginia Marchman](https://profiles.stanford.edu/virginia-marchman), [Tim O'Donnell](http://people.linguistics.mcgill.ca/~timothy.odonnell/), and [Roger Levy](http://www.mit.edu/~rplevy/).

```{r}
subpart_tags <- function(sub) {
  # HTML(glue('<i class="fa fa-{sub$icon}"></i>{sub$text}'))
  tagList(a(class = "subpart-icon", href = sub$url, icon(sub$icon)),
          a(href = sub$url, div(class = "subpart-text", HTML(sub$text))))
}

item_tags <- function(it, sec) {
  # column(
    # width = it$width,
    div(class = glue("bs-callout bs-callout-{sec$color}"),
        div(class = "right",
            map(it$links, \(link) a(href = link$url, icon(link$icon)))),
        a(href = it$url, h4(it$name)),
        if (length(it$with)) {
          div(class = "with", "with ",
              HTML(paste(
                map(it$with, function(w) {
                  if (length(w$url) > 0) glue('<a href="{w$url}">{w$name}</a>') else w$name
                }),
                collapse = ", "
              ))
          )
        },
        # if ("html" %in% names(it) && it$html) HTML(it$text) else p(it$text)
        p(it$description),
        div(class = "subparts", map(it$subparts, subpart_tags))
    )
  # )
}

section_tags <- function(sec) {
  n_items <- length(sec$items)
  sec_items <- map(sec$items, \(i) item_tags(i, sec))
  tagList(
    HTML(glue(
      '<h3><i class="fa fa-{sec$icon} fa-color-{sec$color}"></i>{sec$title}</h3>'
    )),
    fluidRow(column(width = 6, sec_items[1:ceiling(n_items / 2)]),
             column(width = 6, sec_items[(ceiling(n_items / 2) + 1):n_items]))
    # fluidRow(column(width = 6, map(sec$items, \(i) item_tags(i, sec))))
  )
}

div(map(components, section_tags))
```

</div>
