\documentclass[11pt,letter]{moderncv}
\moderncvcolor{blue}
\moderncvstyle{classic}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper,scale=0.825]{geometry} % adjust the page margins 
\usepackage{footmisc} % enabling footnotes

%\setlength{\hintscolumnwidth}{3cm}				% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\hyphenpenalty =10000

\definecolor{color2}{RGB}{75,75,75}
% personal data % options include title, address, mobile, extrainfo, homepage, photo, quote
\name{Mika}{Braginsky}
%\address{710 Rosewood Drive}{Palo Alto, CA 94303}
\email{mika.br@gmail.com}
\homepage{mikabr.github.io}
\phone[mobile]{617-615-6452}
%\social[github]{mikabr} 


\makeatletter
\renewcommand\@biblabel[1]{}
\makeatother

\nopagenumbers{}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
% Note the options here:
% \cvitemwithcomment{}{}{}
% \cvdoubleitem{}{}{}{}
% \cvitem{}{}
% \cvlistitem{}
\begin{document}
\makecvtitle

\vspace*{-2\baselineskip}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\cventry{June 2014}{B.S. in Computer Science and Engineering \& Brain and Cognitive Sciences}
{Massachusetts Institute of Technology}{Cambridge, MA}{\textit{GPA: 4.5/5.0}}{}

%\cventry{June 2010}
%{High School Diploma}
%{Newton South High School}{Newton, MA}{\textit{3.8/4.0}}{}

\vspace*{0.25em}

\section{Research Experience}

%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.

\cventry{\small Sep 2014 \\-- present}
{Language and Cognition Lab}{Stanford University}{\newline Research Assistant}{Advisor: Michael Frank}{
%
Conduct large-scale analyses of language acquisition data, such as composition of vocabulary, relations between grammar and the lexicon, and prediction of words' age of acquisition. Lead development on innovative technical projects including:
\begin{itemize}
\item Wordbank: An open online repository of children's language development data.
\item MetaLab: A tool aggregating meta-analyses of phenomena in the language acquisition literature.
\item Wordful: A mobile app that aims to innovate in the collection of word learning data.
\end{itemize}
%
}
\vspace*{0.2em}

\cventry{\small Sep 2013 \\-- Aug 2014}%{Sep 2013 \\-- Aug 2014}
{Computational Cognitive Science Group}{Massachusetts Institute of Technology}{Undergraduate Researcher}{Advisor: Joshua Tenenbaum}{
%
Developed and implemented a model of early cross-situational word learning using a framework of Bayesian inference.
%
}
\vspace*{0.2em}

\raggedright
\cventry{\small Summer 2013}%{June 2013 \\-- Aug 2013}
{Research and Development Team}{Basis Technology}{R\&D Intern}{}{
%
Improved a statistical model for named-entity resolution and entity linking through error analysis and software development.
%
}
\vspace*{0.2em}

\raggedright
\cventry{\small Spring 2013}%{Apr 2013 \\-- May 2013}
{Psycholinguistics Laboratory Final Project}{Massachusetts Insitute of Technology}{}{Professor: Ted Gibson}{
%
Designed and ran an online experiment examining whether people tend to pick shorter word forms in more predictive global and local contexts.
%
}
\vspace*{0.2em}

\raggedright
\cventry{\small Fall 2012}%{Sep 2012 \\-- Dec 2012}
{Natural Language \& Computer Representation of Knowledge Final Project}{Massachusetts Insitute of Technology}{}{Professor: Robert Berwick}{
%
Implemented a system that solves SAT analogy problems in a cognitively-motivated way.
%
}
%\vspace*{0.2em}
%
%\raggedright
%\cventry{\small Summer 2012}%{June 2012 \\-- Aug 2012}
%{Bioengineering Systems and Technologies Group}{MIT Lincoln Laboratory}{Undergraduate Researcher}{Advisor: Thomas Quatieri}{
%%
%Developed a psycholinguistic behavioral experiment for investigating the connection between language and motor control.
%%
%}

%\vspace*{0.2em}

%\raggedright
%\cventry{Dec 2011}
%{Society of Mind Final Project}{}{}{Professor: Marvin Minsky}{
%
%Designed and ran an experiment exploring how humans approach pathfinding problems in undirected graphs and compared subjects to search algorithms.
%
%}
%\vspace*{0.25em}

%\raggedright
%\cventry{\small Fall 2010}%{Sep 2010 \\-- Jan 2011}
%{Quantitative Research in Linguistics Group}{Massachusetts Institute of Technology}{Undergraduate Researcher}{Advisor: Peter Graff}{
%%
%Designed an online experiment for comparing the learnability of different word order patterns.
%%
%}

\vspace*{0.25em}

\section{Skills}
\cvitem{Programming}{\small Proficient in R, Python, JavaScript; familiar with SQL, Java, MATLAB, Scheme.}
%\cvline{Systems}{\small Linux, OSX, Windows, Android}
\cvitem{Tools}{\small Linux, Git, Subversion, EC2, Apache, HTML, CSS, \LaTeX.}
%Django framework
\cvitem{Languages}{\small Native English and Russian, conversational Hebrew.}

\vspace*{0.25em}

%\printbibliography[heading=subbibliography,title={{\small Publications}}, type=article, prefixnumbers={B}]
%\printbibliography[heading=subbibliography,title={{\small Journals}},type=article,prefixnumbers={J}]

%\section{Publications}
\renewcommand{\refname}{Publications}

\begin{small}
\begin{thebibliography}{}

\bibitem[\protect\astroncite{Frank et~al.}{view}]{frank2015wordbank:-an-op}
Frank, M.~C., \textbf{Braginsky, M.}, Yurovsky, D., and Marchman, V.~A. (in press).
\newblock Wordbank: An open repository for developmental vocabulary data. Journal of Child Language.

\bibitem[\protect\astroncite{Braginsky
  et~al.}{2015}]{braginsky2015developmental-c}
\textbf{Braginsky, M.}, Yurovsky, D., Marchman, V.~A., and Frank, M.~C. (2015).
\newblock Developmental changes in the relationship between grammar and the
  lexicon.
\newblock In {\em Proceedings of the 37th Annual Conference of the Cognitive
  Science Society}.

\end{thebibliography}
\end{small}

\renewcommand{\refname}{Posters and Talks}

\begin{small}
\begin{thebibliography}{}

\bibitem{icis2016aoapred}
\textbf{Braginsky, M.}, Yurovsky, D., Marchman, V.~A., and Frank, M.~C. (May 2016).
\newblock Predicting Age of Acquisition for Early Words Across Languages.
\newblock Talk to be presented at the XX Biennial International Congress of Infant Studies.
  
\bibitem{bcccd2016metalab}
Tsuji, S., Bergmann, C., Cristia, A., Lewis, M., \textbf{Braginsky, M.}, and Frank, M.~C. (January 2016).
\newblock MetaLab: Power Analysis and Experimental Planning in Developmental Research Made Easy.
\newblock Poster presented by Sho Tsuji at the 2015 Budapest CEU Conference on Cognitive Development.
  Budapest, Hungary.

\bibitem{tubingen2015aoapred}
\textbf{Braginsky, M.}, Yurovsky, D., Marchman, V.~A., and Frank, M.~C. (December 2015).
\newblock Predicting Age of Acquisition for Early Words Across Languages.
\newblock Talk presented at the Studying Language Learning Workshop.
  T{\"u}bingen, Germany.
  
\bibitem{bucld2015vocabcomp}
\textbf{Braginsky, M.}, Yurovsky, D., Marchman, V.~A., and Frank, M.~C. (November 2015).
\newblock Developmental trajectories of vocabulary composition across languages.
\newblock Poster presented at the 40th Annual Boston University
  Conference on Language Development.
  Boston, MA.
  
 \bibitem{bucld2015metalab}
Lewis, M., \textbf{Braginsky, M.}, Bergmann, C., Tsuji, S., Cristia, A., and Frank, M.~C. (November 2015).
\newblock MetaLab: A tool for power analysis and experimental planning in developmental research.
\newblock Talk presented by Molly Lewis at the 40th Annual Boston University
  Conference on Language Development.
  Boston, MA.
  
\bibitem{cogsci2015grammarlex}
\textbf{Braginsky, M.}, Yurovsky, D., Marchman, V.~A., and Frank, M.~C. (July 2015).
\newblock Developmental changes in the relationship between grammar and the
  lexicon.
\newblock Poster presented at the 37th Annual Conference of the Cognitive Science Society.
  Pasadena, CA.

\bibitem{srcd2015wordbank}
Frank, M.~C., Yurovsky, D., Schneider, R., \textbf{Braginsky, M.}, and Marchman, V.~A. (March 2015).
\newblock Studying children's vocabulary development at scale.
\newblock Talk presented by Michael Frank at the 2015 Society for Research in Child
  Development Biennial Meeting.
  Philadephia, PA.

\bibitem{bucld2014wordbank}
Frank, M.~C., Yurovsky, D., Krishna, R., \textbf{Braginsky, M.}, and Marchman, V.~A. (November 2014).
\newblock Wordbank: An open repository for developmental vocabulary data.
\newblock Poster presented by Michael Frank at the 39th Annual Boston University
  Conference on Language Development.
  Boston, MA.
 
\end{thebibliography}
\end{small}


%\nocite{*}
%\bibliographystyle{apa}
%\printbibliography[heading=subbibliography]

%\bibliography{posters}

%\renewcommand{\refname}{Posters}

%\bibliography{posters}

%\renewcommand{\refname}{Publications}
%\bibliography{posters}

\vspace*{0.25em}

\section{Coursework}

\cvitem{}{\textbf{Massachusetts Institute of Technology}}
\vspace*{-0.25em}

\begin{cvcolumns}
 
  \cvcolumn[0.4]{Cognitive Science \& Linguistics}{
  \begin{footnotesize}
  \begin{itemize}
	\item Topics in Language Acquisition% (G)\footnote{1}
	\item Laboratory in Psycholinguistics
	\item Computational Cognitive Science
	\item Semantics and Pragmatics
	\item Phonology
	\item Music Cognition
	\item What Is Intelligence?% (G)
	\item Philosophical Issues in Brain Science
  \end{itemize}
  \end{footnotesize}}

  \cvcolumn{Computer Science \& Mathematics}{
  \begin{footnotesize}
  \begin{itemize}
	\item Practical Natural Language Processing% (G)
	\item Natural Language and the Representation of Knowledge% (G)
%	\item Society of Mind (G)
	\item Artificial Intelligence
%	\item The Human Intelligence Enterprise
	\item Design and Analysis of Algorithms
	\item Computer Systems Engineering
%	\item Elements of Software Construction
%	\item Computation Structures
	\item Introduction to Inference
	\item Probability and Random Variables
	\item Linear Algebra
%	\item Differential Equations
%	\item Mathematics for Computer Science
  \end{itemize}
  \end{footnotesize}}
  
\end{cvcolumns}

\vspace*{-0.25em}

\cvitem{}{\textbf{Linguistic Summer Institute 2015}}
\vspace*{-0.5em}
\begin{cvcolumns}
  \cvcolumn{}{
  \begin{footnotesize}
  \begin{itemize}
	\item Computational Psycholinguistics
	\item Computational Lexical Semantics
	\item Unsupervised Learning of Linguistic Structure: Morphology
	\item Making the Most of Extant Data in Early Language Acquisition Research %From input to production through perception: 
  \end{itemize}
  \end{footnotesize}}
\end{cvcolumns}
	

%\footnotetext[1]{Graduate course}

\section{Teaching Experience}
\cventry{\small Sep 2011 \\-- Dec 2011}
{Laboratory Assistant}{Introduction to Electrical Engineering and Computer Science}{}{}{
%
Assisted the course staff with lab preparation; guided the $\sim$75 students during lab session.
%
}

\cventry{\small Jan 2010 \\-- Dec 2011}
{Afterschool Class Teacher}{Jewish Community Day School}{}{}{
%
Taught elementary and middle school students mathematical thinking through puzzles and games.
%
}

%\cventry{\small Sep 2008 \\-- June 2010}
%{Head Teaching Assistant}{Honors Chemistry, Newton South High School}{}{}{
%%
%Coordinated the $\sim$10 other TAs in grading, tutoring, and laboratory preparation.
%%
%}

\section{Leadership Positions}

\begin{small}
\cvitemwithcomment{}{President, MIT Assassins' Guild}{\small May 2013 -- Aug 2014}
\cvitemwithcomment{}{Vice President and Treasurer, Random Hall}{\small Nov 2012 -- Nov 2013}
\cvitemwithcomment{}{Treasurer, MIT Science Fiction Society}{\small May 2012 -- May 2013}
\cvitemwithcomment{}{Faculty Liaison, MIT Brain and Cognitive Sciences Society}{\small May 2012 -- May 2013}
\end{small}

%\section{Awards and Honors}
%\cventry{2008}{National Merit Finalist}{}{awarded to approximately 15,000 students nationally}{}{}
%\cventry{2008}{National AP scholar}{}{awarded to approximately 12,000 students nationally}{}{}


\end{document}
